### 2020-01-26 paper2/paper.tex
abstract (eng)

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, I performed a series of simulations, using methods developed in paper 1, to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment. The main objective was to elucidate the physical mechanism that leads to the experimentally observed droplet clustering, which had been explained by a dipolar interaction theory. Contrary to previous belief, we found that dipolar interactions alone cannot account for the fast droplet dynamics; a number of 3D effects must be included to faithfully reproduce the observation. This conclusion is supported by theoretical derivations of the Stokes flow (papers 3 and 4), implying that designing microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
Self-assembly of soft matter, such as droplets or colloids, has become a promising scheme to engineer novel materials, model living matter, and explore non-equilibrium statistical mechanics. In this article, we present detailed numerical simulations of few non-Brownian droplets in various flow conditions, specifically, focusing on their self-assembly within a short distance in a three-dimensional ($3D$) microfluidic channel, cf.\
\cite{tabeling}.
%[Shen \textit{et al., Adv. Sci.}, 2016, \textbf{3}(6):1600012].
Contrary to quasi two-dimensional ($q2D$) systems, where dipolar interaction is the key mechanism for droplet rearrangement, droplets in $3D$ confinement produce much less disturbance to the underlying flow, thus experiencing weaker dipolar interactions. Using confined simple shear and Poiseuille flows as reference flows, we show that the droplet dynamics is mostly affected by the shear-induced cross-stream migration, which favors chain structures if the droplets are under an attractive depletion force. For more compact clusters, such as three droplets in a triangular shape, our results suggest that an inhomogeneous cross-sectional inflow profile is further required. Overall, the accelerated self-assembly of a small-size droplet cluster results from the combined effects of strong depletion forces, confinement-mediated shear alignments, and fine-tuned inflow conditions. The deterministic nature of the flow-assisted self-assembly implies the possibility of large throughputs, though calibration of all different effects \xx{to directly produce large droplet crystals is generally difficult}.
\end{paperabstract}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Flow-assisted droplet assembly in a 3D microfluidic channel] % Short title used in headlines (optional)
{%
  Flow-assisted droplet assembly in a 3D microfluidic channel% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Flow-assisted droplet assembly in a 3D microfluidic channel} % Title for toc
%
\paperauthor[Ge, Tammisola, Brandt] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge, Outi Tammisola, Luca Brandt%
}%
%
\listpaperauthor{Z. Ge, O. Tammisola, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Soft Matter.] % Short publish info used in List Of Papers
{%
	Soft Matter%
}%
%
\papervolume{15}%
%
\papernumber{}%
%
\paperpages{3451--3460}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
In this paper, we perform a series of simulations, using methods developed in \emph{Paper 1},
to examine the droplet interaction in increasingly realistic conditions, mimicking a microfluidic experiment.
The main objective is to elucidate the physical mechanism that leads to the experimentally observed droplet clustering,
which had been explained by a dipolar interaction theory.
Contrary to previous belief, we find that dipolar interactions alone cannot account for the fast droplet dynamics;
a number of 3D effects must be included to faithfully reproduce the observation.
This conclusion is supported by theoretical derivations of particle interactions in the Stokes flow (\emph{Papers 3 \& 4}),
implying that designing optimal microfluidic channels to directly produce large droplet crystals remains difficult in practice.
}%
%
\graphicspath{{paper2/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

@@

%------------------------------------------------------------------------------
% Abstract
%------------------------------------------------------------------------------
%
\begin{paperabstract}
Self-assembly of soft matter, such as droplets or colloids, has become a promising scheme to engineer novel materials,
model living matter, and explore non-equilibrium statistical mechanics.
In this article, we present detailed numerical simulations of few non-Brownian droplets in various flow conditions,
specifically, focusing on their self-assembly within a short distance in a three-dimensional ($3D$) microfluidic channel, cf.\ \cite{tabeling}.
%[Shen \textit{et al., Adv. Sci.}, 2016, \textbf{3}(6):1600012].
Contrary to quasi two-dimensional ($q2D$) systems, where dipolar interaction is the key mechanism for droplet rearrangement,
droplets in $3D$ confinement produce much less disturbance to the underlying flow, thus experiencing weaker dipolar interactions.
Using confined simple shear and Poiseuille flows as reference flows,
we show that the droplet dynamics is mostly affected by the shear-induced cross-stream migration,
which favors chain structures if the droplets are under an attractive depletion force.
For more compact clusters, such as three droplets in a triangular shape,
our results suggest that an inhomogeneous cross-sectional inflow profile is further required.
Overall, the accelerated self-assembly of a small-size droplet cluster results from the combined effects of
strong depletion forces, confinement-mediated shear alignments, and fine-tuned inflow conditions.
The deterministic nature of the flow-assisted self-assembly implies the possibility of large throughputs,
though calibration of all different effects to directly produce large droplet crystals is generally difficult.
\end{paperabstract}

### 2020-01-26 paper3/paper.tex
abstract (eng)

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   \todo
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Integral representation of channel flow with interacting particles] % Short title used in healines (optional)
{%
 Integral representation of channel flow with interacting particles% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Integral representation of channel flow with interacting particles} % Title for toc
%
\paperauthor[Fouxon, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Zhouyang Ge$^3$, Luca Brandt$^3$, \\Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Phys.\ Rev.\ E.] % Short publish info used in List Of Papers
{%
	Physical Review E%
}%
%
\papervolume{96}%
%
\papernumber{063110}
%
\paperpages{}%
%
\paperyear{2017}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this part one of a two-part theoretical work on droplet interactions,
   we consider the far-field interaction of spherical droplets or particles traveling in the Poiseuille flow.
   A boundary integral representation of the disturbance flow is derived,
   showing that, to leading order, the flow is dipolar and proportional to a weighted integral of the stress and flow at the particle surface.
   We tabulate the dipole moment under various confinement and particle initial positions using direct numerical simulations of the Navier-Stokes equation,
   then introduce and solve the equation of motion that describes hydrodynamic interactions in the special case of two and three particles. 
}%
%
\graphicspath{{paper3/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-01-26 paper4/paper.tex
abstract (eng)

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   \todo
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Two spheres in wall-bounded shear flow] % Short title used in healines (optional)
{%
 The theory of hydrodynamic interaction of \\two spheres in wall-bounded shear flow% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{The theory of hydrodynamic interaction of two spheres in wall-bounded shear flow} % Title for toc
%
\paperauthor[Fouxon, Rubinstein, Ge, Brandt, Leshansky] % Short authors used in headlines and List Of Papers
{%
  Itzhak Fouxon$^{1,2}$, Boris Rubinstein$^3$, Zhouyang Ge$^4$, \\Luca Brandt$^4$, Alexander Leshansky$^1$%
}%
%
\listpaperauthor{I. Fouxon, B. Rubinstein, Z. Ge, L. Brandt, A. Leshansky}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Department of Chemical Engineering, Technion, Haifa 32000, Israel\\%
  $^2$ Department of Computational Science and Engineering, Yonsei University, \\Seoul 120-749, South Korea\\%
  $^3$ Stowers Institute for Medical Research, 1000 E 50th st., Kansas City, \\MO 64110, USA\\%
  $^4$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden%
}%
%
\paperjournal[Under review for Phys.\ Rev.\ Fluids] % Short publish info used in List Of Papers
{%
	Under review for Physical Review Fluids%
}%
%
\papervolume{}%
%
\papernumber{}
%
\paperpages{}%
%
\paperyear{}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In the second part of the two-part theoretical work on droplet interactions in shear flow,
   we revisit the classical work of \cite{batchelor_green_1972}, where two spherical particles interact hydrodynamically in a unbounded linear flow.
   Using the boundary integral formulation derived in \emph{Paper 3},
   we show that the inclusion of a distant wall results in qualitatively different particle trajectories demonstrative of the wall's singular perturbation.
   Specifically, the distance at which the wall significantly alters the particles interaction scales as $z_0^{3/5}$,
   with $z_0$ being the initial distance between the particle and the wall.
   The phase portrait of the particle relative paths admits domains of closed (dancing) and open (swapping) trajectories,
   apart from those that also exist in unbounded shear flows.
   We postulate that this is topologically stable and verified it by direct numerical simulations of the Navier-Stokes equations.
   Qualitatively, the distant wall is the third body that changes the global topology of the phase portrait of two-particle interaction.
}%
%
\graphicspath{{paper4/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-01-26 paper5/paper.tex
abstract (eng)

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
\todo
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Droplets in homogeneous shear turbulence] % Short title used in headlines (optional)
{%
  Droplets in homogeneous shear turbulence% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Droplets in homogeneous shear turbulence} % Title for toc
%
\paperauthor[Rosti, Ge, Jain, Dodd, Brandt] % Short authors used in headlines and List Of Papers
{%
  Marco E. Rosti$^1$, Zhouyang Ge$^1$, Suhas S. Jain$^2$, \\Michael S. Dodd$^2$, Luca Brandt$^{1,3}$%
}%
%
\listpaperauthor{M.E. Rosti, Z. Ge, S.S. Jain, M.S. Dodd, L. Brandt}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Center for Turbulence Research, Stanford University, CA 94305, USA\\%
  $^3$ Department of Energy and Process Engineering, Norwegian University of Science and Technology (NTNU), NO 7491, Norway%
}%
%
\paperjournal[J. Fluid Mech.] % Short publish info used in List Of Papers
{%
	Journal of Fluid Mechanics%
}%
%
\papervolume{876}%
%
\papernumber{}%
%
\paperpages{962--984}%
%
\paperyear{2019}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   This paper reports a simulation study of liquid droplets immersed in another density- and viscosity-matched fluid (5\% volume fraction)
   in homogeneous shear turbulent flow at a shear Reynolds number equal to 15 200.
   Detailed fluid motions are visualised, showing intense deformation, breakup, and coalesence of the droplets as the flow evolves.
   We examine the flow and droplet statistics, including Taylor-microscale Reynolds numbers, turbulent kinetic energy budget, droplet size distributions, etc.,
   under various surface tensions and initial droplet diameters.
   The overall results suggest that the dispersed phase acts as a sink of the turbulent kinetic energy for the carrier fluid, and
   the maximal droplet sizes are predicted by the Hinze scaling despite of droplet coalescence and a mean shear.
}%
%
\graphicspath{{paper5/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

### 2020-01-26 paper6/paper.tex
abstract (eng)

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1,$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
\todo
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}

>>>>

%------------------------------------------------------------------------------
% Define title, author(s), affiliation and publishing status
%
\papertitle[Effective slip over partially filled microcavities] % Short title used in headlines (optional)
{%
  Effective slip over partially filled microcavities and its possible failure% THE COMMENT SYMBOL AT THE END OF THIS LINE IS NEEDED
}%
%
\papertoctitle{Effective slip over partially filled microcavities and its possible failure} % Title for toc
%
\paperauthor[Ge, Holmgren, Kronbichler, Brandt, Kreiss] % Short authors used in headlines and List Of Papers
{%
  Zhouyang Ge$^1$, Hanna Holmgren$^2$, Martin Kronbichler$^3$, \\Luca Brandt$^1,$, Gunilla Kreiss$^2$%
}%
%
\listpaperauthor{Z. Ge, H. Holmgren, M. Kronbichler, L. Brandt, G. Kreiss}% (optional) Short authors used in List Of Papers
%
\paperaffiliation
{%
  $^1$ Linn\'e FLOW Centre and SeRC, KTH Mechanics, S-100 44 Stockholm, Sweden\\%
  $^2$ Division of Scientific Computing, Department of Information Technology, \\Uppsala University, Box 337, 751 05 Uppsala, Sweden\\%
  $^3$ Institute for Computational Mechanics, Technical University of Munich, Boltzmannstrasse 15, 85748 Garching b. München, Germany%
}%
%
\paperjournal[Phys. Rev. Fluids.] % Short publish info used in List Of Papers
{%
	Physical Review Fluids%
}%
%
\papervolume{3}%
%
\papernumber{054201}%
%
\paperpages{}%
%
\paperyear{2018}%
%
\papersummary%
{% Insert summary of the paper here (used in introduction)
   In this paper, we combine two separate simulation methods (phase field and level set methods) to numerically study
   the transverse flow over a 2D model liquid-infused surface (LIS).
   Computationally, we introduce and verifie a multiscale numerical framework for wetting modelling
   by locally solving the Cahn-Hilliard equations near the moving contact line within a larger Stokes system.
   Physically, we conduct a parametric study of the performance of the LIS, quantified by its effective slip length and potential drainage.
   Among the many parameters (the capillary number, viscosity ratio, contact angle, etc.) explored,
   we identify that filling fraction is the most sensitive parameter for the effective slip;
   the effects of other parameters are generally intertwined but weakened if the surface groove is not fully filled.
   Furthermore, we report a shear-driven failure mode associated with lubricant drainage,
   that is worse at higher lubricant viscosities if the lubricant is less viscous than the outer fluid,
   but disappears if the lubricant is more viscous.
   Overall, our study may serve as a conceptual guide for LIS design complementing experimental tests.
}%
%
\graphicspath{{paper6/}}%
%
%
%===============================================================================
%                            BEGIN PAPER
%===============================================================================
%
\begin{paper}
